Trauma treatment delay

### 2023-11-22 manuscriptlongversion.Rmd
text

The results show that generally, patients do not systemically receive
delayed treatment because of a patient level factor. This should be seen
as a good thing, as it suggests that the delayed treatment happens more
at random than because of a factor on a patient level.

@@

20

@@

>>>>

The results show that generally, patients do not systemically receive
delayed treatment because of a patient level factor. In both groups, ISS
had an unadjusted odds ratio of 0.98 and 0.96 respectively. The
disparity between these ORs is because of previously mentioned slightly
different group sizes and patients because of the different patients
being excluded.

@@

The above shown results should be seen as a good thing, as it suggests
that the delayed treatment happens more at random than because of a
factor on a patient level.

@@

Discussing the generalisability of this study, we included the all the
trauma patients treated and Karolinska University Hospital and excluded
40.7% of that population based on that they had not been screened for
ofi. Additional patients were excluded because of missing data, but no
distinct groups except the not screened patients were removed. On that
basis, this population should be a general representation of trauma
patients at the equivalent of a level 1 trauma center, making this study
generalisable.
